Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-20 paper/ijcai/paper.tex
table 4

		\centering
		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
		\vspace{-1cm}

		\caption{Faults of omissions' distribution}
		\label{fig:foos}
\end{figure}

@@

This subsection aims to report the performance of the \ds{} technique on slicing de
faults of $5$ \dfj{} projects. Table \ref{tab:red}
presents the reduction percentage obtained for each project after slicing the top
$5$ and $10$ of classes comprising the highest faulty statements. Our approach was
capable to reduce the \dfj{} projects in an average of $30.23\%$.

@@

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$             & \combpar{5}                 & \combpar{10}                 \\ \midrule
Mean & 580.0 (584.3)   &  502.6 (516.4)  & 567.0 (679.7)  & 491.5 (614.0)   \\ \midrule
Median & 47.5 (49.4)    & 54.5 (53.0) & 42.7 (69.3)  & 40.0 (56.9)\\ \midrule
Variance & 1237.0 (1223.1)  &  1149.1 (1148.1) & 1229.4 (1352.4) &  1143.0 (1294.9) \\ \midrule
Shapiro &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table*}

>>>>

		\centering
		\includegraphics[width=0.42\textwidth]{figures/defects4j.pdf}
		\vspace{-1cm}
		\caption{Faults of omissions' distribution}
		\label{fig:foos}
\end{figure}

@@

This subsection aims to report the performance of the \ds{} technique on slicing de
faults of $5$ \dfj{} projects. Table \ref{tab:red}
presents the reduction percentage obtained for each project after slicing the top
$5$ and $10$ of classes comprising the highest faulty statements. We observed a reduction 
of 30.23\% on average in the projects considered in our study.

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}l|l|l|l|l@{}}
\toprule
  & SFL$^{5}$      & SFL$^{10}$     & \combpar{5}              & \combpar{10}              \\ \midrule
Mean & \textbf{580.0} (584.3)   &  \textbf{502.6} (516.4)  & \textbf{567.0} (679.7)  & \textbf{491.5} (614.0)   \\ \midrule
Median & \textbf{47.5} (49.4)    & \textbf{54.5} (53.0) & \textbf{42.7} (69.3)  & \textbf{40.0} (56.9)\\ \midrule
Variance & \textbf{1237.0} (1223.1)  &  \textbf{1149.1} (1148.1) & \textbf{1229.4} (1352.4) &  \textbf{1143.0} (1294.9) \\ \midrule
Shapiro &\makecell{W = 0.52 \\ p = 1.43 x $10^{-24}$} & \makecell{W = 0.48 \\ p = 2.12 x $10^{-25}$} & \makecell{W = 0.51 \\ p = 1.00 x $10^{-24}$} & \makecell{W = 0.47 \\ p = 1.62 x $10^{-25}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 171.14 \\ p-value = 7.24 x $10^{-37}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests}
  \label{table:st}
\end{table}
